\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}

% Font Setup - Georgia 10pt
\usepackage{fontspec}
\setmainfont{Georgia}[Scale=1.0]

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Margins & Layout
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.0in}
\addtolength{\topmargin}{-0.7in}
\addtolength{\textheight}{1.4in}
\setlength{\footskip}{5.0pt} 

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{\vspace{-5pt}\raggedright\large\bfseries}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-4pt}]

% Custom commands
\newcommand{\resumeItem}[1]{\item\small{#1 \vspace{-2pt}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{@{}l @{\extracolsep{\fill}} r@{}}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}
  \vspace{-7pt}
}
\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{@{}l @{\extracolsep{\fill}} r@{}}
      \small#1 & #2 \\
    \end{tabular*}
    \vspace{-7pt}
}
\newcommand{\resumeAchievementHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}[t]{@{}p{0.85\textwidth} @{\extracolsep{\fill}} r@{}}
      \small#1 & #2 \\
    \end{tabular*}
    \vspace{-7pt}
}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{-2pt}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \textmd{\textbf{Somanshu Mohapatra}}} \\ \vspace{4pt}
    \small \faPhone\ \href{tel:+917982305740}{+91 7982305740} ~ 
    \href{mailto:somanshu025@gmail.com}{\faEnvelope\ somanshu025@gmail.com} ~ 
    \href{https://linkedin.com/in/somanshu-mohapatra}{\faLinkedin\ linkedin.com/in/somanshu-mohapatra} ~
    \href{https://github.com/som-anshu}{\faGithub\ github.com/som-anshu}
\end{center}
\vspace{-8pt}

%-----------SKILLS-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Robotics:}{ Forward/Inverse Kinematics (DH Parameters), ROS2, RViz2, MoveIt, Gazebo, Path Planning, Motion Control, PID Control, Sensor Fusion, SLAM.} \\
     \textbf{Electronics:}{ Arduino UNO, Raspberry Pi, STM32, ATmega328P, RP2040, Motor Drivers, Serial Communication (UART, I2C, SPI), LabVIEW, Proteus, NGspice, Pspice.} \\
     \textbf{AI \& Vision:}{ AIML, Deep Learning (PyTorch, TensorFlow, CNN, YOLO), OpenCV, OpenVINO, AI Image Generation (Stable Diffusion, AUTOMATIC1111, Illustrious Models).} \\
     \textbf{CAD \& Design:}{ SolidWorks, Fusion 360, AutoCAD, Creo Parametric, ANSYS HFSS, Assembly Design, Rapid Prototyping, 3D Printing (FDM/SLA), Bambu Slicer, LightBurn.} \\
     \textbf{Languages:}{ C++, Python, Java, JavaScript, HTML, SQL, Embedded C, MATLAB, GNU Octave.} \\
     \textbf{Soft Skills:}{ Effective Organizer, Team Management, Strong Interpersonal Skills, Problem Solving.}
    }}
 \end{itemize}
\vspace{-8pt}

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{\href{https://github.com/som-anshu/2.4GHz-microstrip-patch-antenna}{2.4GHz Microstrip Patch Antenna}} $|$ \emph{ANSYS HFSS}}{Oct' 25}
          \resumeItemListStart
            \resumeItem{Designed and simulated a high-frequency microstrip patch antenna optimized for 2.4GHz wireless communication applications.}
            \resumeItem{Conducted electromagnetic field analysis using ANSYS HFSS to evaluate return loss, gain, and radiation patterns.}
            \resumeItem{Optimized physical dimensions and substrate selection to achieve superior impedance matching and antenna efficiency.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{\href{https://github.com/som-anshu/damn}{Dynamic Audio Monitoring and Narration}} $|$ \emph{Raspberry Pi, Python, AssemblyAI API}}{May' 25}
          \resumeItemListStart
            \resumeItem{Developed a real-time transcription system for the deaf using Raspberry Pi to provide accessible communication.}
            \resumeItem{Integrated AssemblyAI API and WebSockets with an I2C SSD1306 OLED display utilizing multi-threading technology.}
            \resumeItem{Optimized inference speeds on Raspberry Pi 4B by deploying an Intel AI Accelerator, significantly reducing latency.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{\href{https://github.com/som-anshu/MATLAB-controlled-robotic-manipulator}{3-DOF Robotic Arm with Real-Time Control}} $|$ \emph{MATLAB, SolidWorks, Arduino IDE, Bambu Studio}}{Apr' 24}
          \resumeItemListStart
            \resumeItem{Constructed a 3-DOF robotic arm utilizing 3D-printed parts to optimize the payload-to-weight ratio for automated tasks.}
            \resumeItem{Programmed real-time motor control via MATLAB-UART communication, enabling precise joint actuation.}
            \resumeItem{Targeted future implementation of Forward and Inverse Kinematics to automate complex trajectory planning.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{\href{https://github.com/som-anshu/python-mysql-accounting}{Python-SQL Accounting Software}} $|$ \emph{Python, MySQL, CLI}}{Jun' 23}
          \resumeItemListStart
            \resumeItem{Engineered a database-driven accounting CLI application to manage financial records and client transactions.}
            \resumeItem{Implemented CRUD operations using Python-MySQL connectivity to facilitate seamless data management.}
            \resumeItem{Provided a robust interface for searching records by client name or date, streamlining data retrieval.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------TRAININGS-----------
\section{Trainings}
  \resumeSubHeadingListStart
    \resumeProjectHeading
      {\textbf{\href{https://drive.google.com/file/d/1PUqcvq8SkgS4APbpqYSwzsYsXNxvOywR/view?usp=drive_link}{AutomateX: Mastering PLCs for Industrial Automation}} $|$ \emph{LPU}}{Mar' 25}
      \resumeItemListStart
        \resumeItem{Acquired comprehensive knowledge of PLC architecture, ladder logic programming, and industrial automation principles.}
        \resumeItem{Simulated automated industrial workflows using TwidoSuite to manage sensor inputs and heavy actuator outputs.}
        \resumeItem{Tested fail-safe mechanisms and sequence patterns to reinforce practical understanding of factory floor operations.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------CERTIFICATES-----------
\section{Certificates}
    \resumeSubHeadingListStart
      \resumeProjectHeading
        {\textbf{\href{https://drive.google.com/file/d/1cPZTNh-I-6y_1j0XR1dyLbr4Padv7GvN/view?usp=drive_link}{Data Base Management System}} $|$ \emph{NPTEL}}{Aug' 25}
      \resumeProjectHeading
        {\textbf{\href{https://drive.google.com/file/d/16txdJfMjoQ9aB_c2yHVEDFoT7vu3QOEp/view?usp=drive_link}{Fusioncraft}} $|$ \emph{Resolute Lab}}{Mar' 24}
    \resumeSubHeadingListEnd

%-----------ACHIEVEMENTS-----------
\section{Achievements}
    \resumeSubHeadingListStart
      \resumeAchievementHeading
        {\textbf{\href{https://drive.google.com/file/d/1PNy_NGYBe1Dt2zS2FtCkgpTa2ak69WHM/view?usp=drive_link}{Patent: Method for Enhancing Food Accessibility and Energy Efficiency in Refrigeration}}}{Sep' 25}
      \vspace{-2pt}
      \resumeItemListStart
        \resumeItem{Application No.: 202511085342 A}
      \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Lovely Professional University}{Phagwara, Punjab}
      {BTech Robotics and Automation; CGPA: 8.38}{Aug' 23 -- Present}
    \resumeSubheading
      {Shri S.N. Siddeshwar Public School}{Gurugram, Haryana}
      {Intermediate, PCMB; Percentage: 85.6\%}{Mar' 21 -- May' 23}
    \resumeSubheading
      {Ryan International School}{Gurugram, Haryana}
      {Matriculation; Percentage: 81.6\%}{Mar' 20 -- May' 21}
  \resumeSubHeadingListEnd

\end{document}