\documentclass[10pt,a4paper]{article}

% Packages
\usepackage[left=0.4in,top=0.4in,right=0.4in,bottom=0.4in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{tabularx}

% Font Setup for Georgia (Compile with XeLaTeX or LuaLaTeX)
\usepackage{fontspec}
\setmainfont{Georgia}

% Color Configurations
\definecolor{resblue}{HTML}{2B3E94} % Deep sapphire blue
\hypersetup{hidelinks} 

% Formatting
\setlength{\parindent}{0pt}
\pagestyle{empty}

% Section Heading Setup
\newcommand{\resumeheading}[1]{
    \vspace{5pt}
    {\large\textbf{\color{resblue} #1}}
    \vspace{1pt}
    {\color{resblue}\hrule height 0.5pt}
    \vspace{4pt}
}

\begin{document}

%----------------------------------------------------------------------------------------
% HEADER
%----------------------------------------------------------------------------------------
{\LARGE\textbf{\color{resblue} Somanshu Mohapatra}}
\vspace{3pt}

\begin{tabularx}{\textwidth}{@{}X r@{}}
\textbf{LinkedIn:} \href{https://linkedin.com/in/som-anshu}{www.linkedin.com/in/somanshu-mohapatra} & \textbf{Email:} \href{mailto:somanshu025@gmail.com}{somanshu025@gmail.com} \\
\textbf{GitHub:} \href{https://github.com/som-anshu}{github.com/som-anshu} & \textbf{Mobile:} \href{tel:+917982305740}{+91 7982305740}
\end{tabularx}

%----------------------------------------------------------------------------------------
% TECHNICAL SKILLS
%----------------------------------------------------------------------------------------
\resumeheading{SKILLS}

\begin{tabularx}{\textwidth}{@{}p{3.2cm} X@{}}
    \textbf{\color{resblue} Languages:} & Experienced in C++, Python, Embedded C, and MATLAB for algorithm development and simulation. \\
    \textbf{\color{resblue} Robotics:} & Applied Forward/Inverse Kinematics (DH Parameters), ROS, and Gazebo for path planning and SLAM. \\
    \textbf{\color{resblue} Electronics:} & Configured Arduino UNO, Raspberry Pi, STM, and motor drivers utilizing UART, I2C, SPI, and CAN. \\
    \textbf{\color{resblue} CAD \& Design:} & Designed assemblies using SolidWorks and Fusion, applying FEA and FDM/SLA printing for prototyping. \\
    \textbf{\color{resblue} Soft Skills:} & Effective Organizer, Team Management, Strong Interpersonal Skills, and logical Problem Solving.
\end{tabularx}

%----------------------------------------------------------------------------------------
% TRAININGS
%----------------------------------------------------------------------------------------
\resumeheading{TRAININGS}

\begin{tabularx}{\textwidth}{@{}X r@{}}
\textbf{\color{resblue} AutomateX: Mastering PLCs for Industrial Automation} $|$ \textit{LPU} & Mar' 25
\end{tabularx}
\textit{\href{https://drive.google.com/file/d/1PUqcvq8SkgS4APbpqYSwzsYsXNxvOywR/view?usp=drive_link}{View Training Certificate}}
\begin{itemize}[leftmargin=1.5em, itemsep=0pt, parsep=1pt, topsep=2pt]
    \item Acquired comprehensive knowledge of PLC architecture, ladder logic programming, and industrial automation principles.
    \item Simulated automated industrial workflows using TwidoSuite to manage sensor inputs and heavy actuator outputs.
    \item Tested fail-safe mechanisms and sequence patterns to reinforce practical understanding of factory floor operations.
\end{itemize}

%----------------------------------------------------------------------------------------
% KEY PROJECTS
%----------------------------------------------------------------------------------------
\resumeheading{PROJECTS}

\begin{tabularx}{\textwidth}{@{}X r@{}}
\textbf{\color{resblue} \href{https://github.com/som-anshu/damn}{Dynamic Audio Monitoring and Narration}} $|$ \textit{Raspberry Pi, Python, AssemblyAI API} & Apr' 25 -- May' 25
\end{tabularx}
\begin{itemize}[leftmargin=1.5em, itemsep=0pt, parsep=1pt, topsep=2pt]
    \item Developed a real-time transcription system for the deaf using Raspberry Pi to provide accessible communication.
    \item Integrated AssemblyAI API and WebSockets with an I2C SSD1306 OLED display utilizing multi-threading technology.
    \item Achieved 95\%+ transcription accuracy and under 300ms latency, enabling practical, on-the-go conversational assistance.
\end{itemize}

\vspace{2pt}

\begin{tabularx}{\textwidth}{@{}X r@{}}
\textbf{\color{resblue} \href{https://github.com/som-anshu/MATLAB-controlled-robotic-manipulator}{3-DOF Robotic Arm with Real-Time Control}} $|$ \textit{MATLAB, SolidWorks, Arduino IDE, Bambu Studio} & Apr' 24
\end{tabularx}
\begin{itemize}[leftmargin=1.5em, itemsep=0pt, parsep=1pt, topsep=2pt]
    \item Constructed a 3-DOF robotic arm utilizing 3D-printed parts to optimize the payload-to-weight ratio for automated tasks.
    \item Programmed NEMA steppers and Arduino Mega, executing forward and inverse kinematics through MATLAB-UART integration.
    \item Decreased trajectory error by 20\% during real-time operations, ensuring precise and reliable object manipulation.
\end{itemize}

\vspace{2pt}

\begin{tabularx}{\textwidth}{@{}X r@{}}
\textbf{\color{resblue} \href{YOUR_GITHUB_LINK_HERE}{Smart Energy Meter}} $|$ \textit{ESP32, IOT Monitoring, HTML Webserver} & Jun' 23
\end{tabularx}
\begin{itemize}[leftmargin=1.5em, itemsep=0pt, parsep=1pt, topsep=2pt]
    \item Designed an IOT-based energy monitoring system to track residential power consumption through a real-time browser interface.
    \item Configured ESP32 and WIFI modules with ZMPT101B and ZMCT103C sensors, transmitting data to an HTML webserver.
    \item Delivered voltage and current measurements with precise accuracy, facilitating efficient remote energy management.
\end{itemize}

%----------------------------------------------------------------------------------------
% CERTIFICATES
%----------------------------------------------------------------------------------------
\resumeheading{CERTIFICATES}

\begin{tabularx}{\textwidth}{@{}X r@{}}
\textbf{\color{resblue} Data Base Management System} $|$ \href{https://drive.google.com/file/d/1cPZTNh-I-6y_1j0XR1dyLbr4Padv7GvN/view?usp=drive_link}{NPTEL} & Aug' 25 \\ [1.5pt]
\textbf{\color{resblue} Fusioncraft} $|$ \href{https://drive.google.com/file/d/16txdJfMjoQ9aB_c2yHVEDFoT7vu3QOEp/view?usp=drive_link}{Resolute Lab} & Mar' 24
\end{tabularx}

%----------------------------------------------------------------------------------------
% ACHIEVEMENTS
%----------------------------------------------------------------------------------------
\resumeheading{ACHIEVEMENTS}

\begin{tabularx}{\textwidth}{@{}X r@{}}
\textbf{\color{resblue} \href{https://drive.google.com/file/d/1PNy_NGYBe1Dt2zS2FtCkgpTa2ak69WHM/view?usp=drive_link}{METHOD FOR ENHANCING FOOD ACCESSIBILITY, MONITORING FRESHNESS,}} & Sep' 25 \\
\textbf{\color{resblue} \href{https://drive.google.com/file/d/1PNy_NGYBe1Dt2zS2FtCkgpTa2ak69WHM/view?usp=drive_link}{AND REDUCING ENERGY LOSS IN CYLINDRICAL REFRIGERATION UNITS}} & 
\end{tabularx}
Somanshu Mohapatra, Dr. Sumit Shoor \\
Application No.: 202511085342 A

%----------------------------------------------------------------------------------------
% EDUCATION
%----------------------------------------------------------------------------------------
\resumeheading{EDUCATION}

\begin{tabularx}{\textwidth}{@{}X r@{}}
\textbf{\color{resblue} Lovely Professional University} & Phagwara, Punjab \\
Bachelor of Technology & Aug' 23 -- Present \\
Robotics and Automation Engineering; CGPA: 8.38 & \\[3pt]
\textbf{\color{resblue} Shri S.N. Siddeshwar Public School} & Gurugram, Haryana \\
Intermediate, PCMB; Percentage: 85.6\% & Mar' 21 -- May' 23 \\[3pt]
\textbf{\color{resblue} Ryan International School} & Gurugram, Haryana \\
Matriculation, Percentage: 81.6\% & Mar' 20 -- May' 21
\end{tabularx}

\end{document}