\documentclass[10pt,a4paper]{article}

% Packages
\usepackage[left=0.4in,top=0.4in,right=0.4in,bottom=0.4in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{tabularx}

% Font Setup for Georgia
\usepackage{fontspec}
\setmainfont{Georgia}

% Color Configurations
\definecolor{resblue}{HTML}{2B3E94}
\hypersetup{hidelinks} 

% Formatting
\setlength{\parindent}{0pt}
\pagestyle{empty}

% Section Heading Setup
\newcommand{\resumeheading}[1]{
    \vspace{8pt}
    {\large\textbf{\color{resblue} #1}}
    \vspace{1pt}
    {\color{resblue}\hrule height 0.5pt}
    \vspace{4pt}
}

\begin{document}

% HEADER
{\LARGE\textbf{\color{resblue} Somanshu Mohapatra}}
\vspace{3pt}

\begin{tabularx}{\textwidth}{@{}X r@{}}
LinkedIn: \href{https://linkedin.com/in/somanshu-mohapatra}{www.linkedin.com/in/somanshu-mohapatra} & Email: \href{mailto:somanshu025@gmail.com}{somanshu025@gmail.com} \\
GitHub: \href{https://github.com/som-anshu}{github.com/som-anshu} & Mobile: \href{tel:+917982305740}{+91 7982305740}
\end{tabularx}

% SKILLS
\resumeheading{SKILLS}
\begin{tabularx}{\textwidth}{@{}p{3.2cm} X@{}}
    \textbf{\color{resblue} Languages:} & C++, Python, Java, JavaScript, HTML, SQL, Embedded C, MATLAB, GNU Octave. \\
    \textbf{\color{resblue} AI \& Vision:} & AIML, Deep Learning (PyTorch, TensorFlow, CNN, YOLO), OpenCV, OpenVINO, AI Image Generation (Stable Diffusion, AUTOMATIC1111). \\
    \textbf{\color{resblue} Robotics:} & Forward/Inverse Kinematics (DH Parameters), ROS2, RViz2, MoveIt, Gazebo, Path Planning, Motion Control, PID Control, Sensor Fusion, SLAM. \\
    \textbf{\color{resblue} Electronics:} & Arduino UNO, Raspberry Pi, STM32, ATmega328P, RP2040, Motor Drivers, Serial Communication (UART, I2C, SPI), LabVIEW, Proteus, NGspice. \\
    \textbf{\color{resblue} CAD \& Design:} & SolidWorks, Fusion 360, AutoCAD, Creo Parametric, ANSYS HFSS, Rapid Prototyping, 3D Printing (FDM/SLA), Bambu Slicer, LightBurn. \\
    \textbf{\color{resblue} Soft Skills:} & Leadership, Strategic Planning, Cross-functional Collaboration, Analytical Problem-Solving.
\end{tabularx}

% TRAININGS
\resumeheading{TRAININGS}
\begin{tabularx}{\textwidth}{@{}X r@{}}
\textbf{\color{resblue} \href{https://drive.google.com/file/d/1PUqcvq8SkgS4APbpqYSwzsYsXNxvOywR/view?usp=drive_link}{AutomateX: Mastering PLCs for Industrial Automation}} $|$ \textit{LPU} & Mar' 25
\end{tabularx}
\begin{itemize}[leftmargin=1.5em, itemsep=2pt, parsep=1pt, topsep=2pt]
    \item Gained expertise in PLC architecture, ladder logic, and industrial automation standards.
    \item Modeled automated workflows in TwidoSuite, managing sensor integration and high-power actuators.
    \item Validated fail-safe protocols and sequence patterns to ensure operational reliability.
\end{itemize}

% PROJECTS
\resumeheading{PROJECTS}
\begin{tabularx}{\textwidth}{@{}X r@{}}
\textbf{\color{resblue} \href{https://github.com/som-anshu/2.4GHz-microstrip-patch-antenna}{2.4GHz Microstrip Patch Antenna}} $|$ \textit{ANSYS HFSS} & Oct' 25
\end{tabularx}
\begin{itemize}[leftmargin=1.5em, itemsep=2pt, parsep=2pt, topsep=3pt]
    \item Designed a high-frequency antenna for 2.4GHz wireless communication standards.
    \item Performed electromagnetic field analysis via ANSYS HFSS to assess return loss, gain, and radiation behavior.
    \item Refined substrate selection and dimensions to maximize impedance matching and antenna efficiency.
\end{itemize}

\vspace{6pt}
\begin{tabularx}{\textwidth}{@{}X r@{}}
\textbf{\color{resblue} \href{https://github.com/som-anshu/damn}{Dynamic Audio Monitoring and Narration}} $|$ \textit{Raspberry Pi, Python, AssemblyAI API} & May' 25
\end{tabularx}
\begin{itemize}[leftmargin=1.5em, itemsep=2pt, parsep=2pt, topsep=3pt]
    \item Engineered a real-time transcription system for the hearing impaired using Raspberry Pi.
    \item Integrated AssemblyAI API and WebSockets with an I2C SSD1306 OLED display using multi-threading.
    \item Reduced latency by deploying an Intel AI Accelerator on Raspberry Pi 4B for accelerated inference.
\end{itemize}

\vspace{6pt}
\begin{tabularx}{\textwidth}{@{}X r@{}}
\textbf{\color{resblue} \href{https://github.com/som-anshu/MATLAB-controlled-robotic-manipulator}{3-DOF Robotic Arm with Real-Time Control}} $|$ \textit{MATLAB, SolidWorks, Arduino} & Apr' 24
\end{tabularx}
\begin{itemize}[leftmargin=1.5em, itemsep=2pt, parsep=2pt, topsep=3pt]
    \item Fabricated a 3-DOF arm using 3D-printed components to improve the payload-to-weight ratio.
    \item Configured real-time motor control via MATLAB-UART communication for precise joint actuation.
    \item Developed a framework for future Forward and Inverse Kinematics integration to enable automated trajectory planning.
\end{itemize}

\vspace{6pt}
\begin{tabularx}{\textwidth}{@{}X r@{}}
\textbf{\color{resblue} \href{https://github.com/som-anshu/python-mysql-accounting}{Python-SQL Accounting Software}} $|$ \textit{Python, MySQL, CLI} & Jun' 23
\end{tabularx}
\begin{itemize}[leftmargin=1.5em, itemsep=2pt, parsep=2pt, topsep=3pt]
    \item Built a database-driven CLI application for financial record and transaction management.
    \item Executed CRUD operations using Python-MySQL connectivity to ensure efficient data handling.
    \item Implemented search functionality by client name and date, streamlining data retrieval.
\end{itemize}

% CERTIFICATES
\resumeheading{CERTIFICATES}
\vspace{4pt}
\begin{tabularx}{\textwidth}{@{}X r@{}}
\textbf{\color{resblue} \href{https://drive.google.com/file/d/1cPZTNh-I-6y_1j0XR1dyLbr4Padv7GvN/view?usp=drive_link}{Data Base Management System}} $|$ \textit{NPTEL} & Aug' 25 \\ [4pt]
\textbf{\color{resblue} \href{https://drive.google.com/file/d/16txdJfMjoQ9aB_c2yHVEDFoT7vu3QOEp/view?usp=drive_link}{Fusioncraft}} $|$ \textit{Resolute Lab} & Mar' 24
\end{tabularx}

% ACHIEVEMENTS
\resumeheading{ACHIEVEMENTS}
\begin{tabularx}{\textwidth}{@{}X r@{}}
\textbf{\color{resblue} \href{https://drive.google.com/file/d/1PNy_NGYBe1Dt2zS2FtCkgpTa2ak69WHM/view?usp=drive_link}{Patent: Method for Enhancing Food Accessibility and Energy Efficiency in Refrigeration}} & Sep' 25 \\
\end{tabularx}
Application No.: 202511085342 A

% EDUCATION
\resumeheading{EDUCATION}
\vspace{4pt}
\begin{tabularx}{\textwidth}{@{}X r@{}}
\textbf{\color{resblue} Lovely Professional University} & Phagwara, Punjab \\
BTech Robotics and Automation; CGPA: 8.38 & Aug' 23 -- Present \\[6pt]
\textbf{\color{resblue} Shri S.N. Siddeshwar Public School} & Gurugram, Haryana \\
Intermediate, PCMB; Percentage: 85.6\% & Mar' 21 -- May' 23 \\[6pt]
\textbf{\color{resblue} Ryan International School} & Gurugram, Haryana \\
Matriculation; Percentage: 81.6\% & Mar' 20 -- May' 21
\end{tabularx}

\end{document}